\maketitle
\toc

\newpage
\pagestyle{preface}


\subsubsection*{ABOUT THIS BOOK}

This book describes how to troubleshoot, adjust, and repair the VAXstation
2000 and the MicroVAX 2000 Workstation to the field replaceable unit (FRU)
level in the field. It covers all FRU options presently available for these two
Systems.

\begin{itemize}
\item \hyperlink{chapter.1}{Chapter 1} contains a System overview that outlines the components of the VAXstation 2000 and MicroVAX 2000 Systems.

\item \hyperlink{chapter.2}{Chapter 2} contains testing and troubleshooting procedures to help iso-
late the problem to an FRU.
\item \hyperlink{chapter.3}{Chapter 3} contains FRU removal and replacement procedures.
\item \hyperlink{chapter.4}{Chapter 4} contains video monitor adjustment procedures for the VAX station 2000 monitor.
\item \hyperlink{chapter.5}{Chapter 5} contains installation instructions for each option available on both the VAXstation 2000 and the MicroVAX 2000.
\item \hyperlink{appendix.a}{Appendix A} contains a list of the test commands.
\item \hyperlink{appendix.b}{Appendix B} contains a complete listing and definitions of the console commands.
\item \hyperlink{appendix.c}{Appendix C} contains a complete listing and definitions of the console messages.
\item \hyperlink{appendix.d}{Appendix D} contains a complete listing and definitions of the VMB boot error Status codes.

\end{itemize}

The detailed \hyperlink{sec:index}{index} and \hyperlink{sec:glossary}{glossary} also help you find Information.

\textbf{Notes, Cautions, and Warnings}

Notes, cautions, and warnings appear throughout this book.

\begin{itemize}
\item Notes contain general, supplemental Information about a topic.
\item Cautions contain information to prevent damage to equipment.
\item Warnings contain information to prevent personal injury.
\end{itemize}
\newpage
\subsubsection*{REFERENCE MANUALS}
\begin{tabularx}{\textwidth}{l l}
\hline
\textbf{Manual} & \textbf{Order Number} \\
\hline
VAXstation 2000 Hardware Installation Guide & \pdf{EK-VAXAA-IN} \\
VAXstation 2000 Owner's Manual & \pdf{EK-VAXAA-OM} \\
VAXstation 2000/MicroVAX 2000 Technical Manual & \pdf{EK-VTTAA-TM} \\
MicroVAX 2000 Hardware Installation Guide & \pdf{EK-MVXAA-IN} \\
MicroVAX 2000 Owner's Manual & \pdf{EK-MVXAA-OM} \\
VR290 Service Guide & \pdf{EK-VR290-SM} \\
VAXstation 2000, MicroVAX 2000, VAXmate Network Guide & \pdf{EK-NETAA-UG} \\
RD53 Technical Description Manual & \pdf{EK-RD53A-TD} \\
RX33 Technical Description Manual & \pdf{EK-RX33T-TM} \\
TZK50/SCSI Controller Technical Manual & \pdf{EK-TZK50-TM} \\
\hline

\end{tabularx}

\subsubsection*{TOOLS AND MATERIALS}
You will need the following tools and materials to service the VAXstation
2000 and MicroVAX 2000 Systems.

\begin{itemize}
\item Field Service Tool Kits

50 Hz Tool Kit p/n 29-23270-00\\
60 Hz Tool Kit p/n 29-23268-00

\item VR260 Video Monitor Tools

Metric Measuring Tape p/n 29-25342-00\\
High-Voltage Anode Discharge Tool p/n 29-24717-00

\item ThinWire Ethernet Tools

Face Plate Installation Kit p/n H8242
\end{itemize}

